\texttt{SuperScreen}: An open-source package for simulating the magnetic response of 2D superconductors

### 2021-08-02 main_cpc.tex
Updates from Overleaf

\begin{figure}
\centering
\begin{subfigure}{.45\textwidth}
  \centering
  \includegraphics[width=\linewidth]{examples/images/ring/circular_ring_mesh.png}
  \caption{A subfigure}
  \label{fig:circular_ring_mesh}
\end{subfigure}%
\begin{subfigure}{.45\textwidth}
  \centering
  \includegraphics[width=\linewidth]{examples/images/ring/square_ring_mesh.png}
  \caption{A subfigure}
  \label{fig:square_ring_mesh}
\end{subfigure}
\caption{A figure with two subfigures}
\label{fig:ring_mesh}
\end{figure}

@@

>>>>

\begin{figure}
\centering
\begin{subfigure}{.4\textwidth}
  \centering
  \includegraphics[width=\linewidth]{examples/images/ring/circular_ring_mesh.png}
  \caption{Circular ring, \mintinline{python}{optimesh_steps=400}.}
  \label{fig:circular_ring_mesh}
\end{subfigure}%
\begin{subfigure}{.4\textwidth}
  \centering
  \includegraphics[width=\linewidth]{examples/images/ring/square_ring_mesh.png}
  \caption{Square ring, \mintinline{python}{optimesh_steps=400}.}
  \label{fig:square_ring_mesh}
\end{subfigure}
\begin{subfigure}{.4\textwidth}
  \centering
  \includegraphics[width=\linewidth]{examples/images/ring/circular_ring_mesh_no_optimesh.png}
  \caption{Circular ring, \mintinline{python}{optimesh_steps=None}.}
  \label{fig:circular_ring_mesh_no_opt}
\end{subfigure}%
\begin{subfigure}{.4\textwidth}
  \centering
  \includegraphics[width=\linewidth]{examples/images/ring/square_ring_mesh_no_optimesh.png}
  \caption{Square ring, \mintinline{python}{optimesh_steps=None}.}
  \label{fig:square_ring_mesh_no_opt}
\end{subfigure}
\caption{Device geometry and mesh for a circular and square ring generated using Code Blocks~\ref{code:device} and \ref{code:mesh_generation}, with (top row) and without (bottom row) \mintinline{python}{optimesh} optimization.}
\label{fig:ring_mesh}
\end{figure}

@@

For example, Code Block~\ref{code:ring_circulating_current} solves two models involving the \mintinline{python}{ring} device. First, Meissner screening of a spatially uniform applied magnetic field, and second, the response of the ring to trapped flux with an associated circulating current of 1 mA with no applied magnetic field. The resulting sheet current and magnetic field distributions can be visualized using the \mintinline{python}{plot_current()} and \mintinline{python}{plot_fields()} methods, which produce the images shown in Figure~\ref{fig:ring_plot_fields_currents}.

\begin{code}
\begin{minted}[fontsize=\footnotesize]{python}
# Simulate the response to a uniform applied field of 0.2 mT
applied_field = sc.sources.ConstantField(0.2)
field_units = "mT"

solutions = sc.solve(
    device=ring,
    applied_field=applied_field,
    field_units=field_units,
)
assert len(solutions) == 1 # Since there is only one layer
uniform_field = solutions[-1]

# Simulate a current circulating around the hole in the ring.
circulating_currents = {"hole": "1 mA"}

solutions = sc.solve(
    device=ring,
    applied_field=None,
    circulating_currents=circulating_currents
)
assert len(solutions) == 1 # Since there is only one layer
trapped_flux = solutions[-1]

for solution in (uniform_field, trapped_flux):
    solution.plot_currents(
        figsize=(6, 7), cross_section_ys=[0], units="mA/um",
    )
    solution.plot_fields(figsize=(6, 7), cross_section_ys=[0])
\end{minted}
\captionof{listing}{Solve for the current and magnetic field distributions resulting from a total current of 1 mA flowing in our \mintinline{python}{ring} device.}
\label{code:ring_circulating_current}
\end{code}

% \begin{code}
% \begin{minted}[fontsize=\footnotesize]{python}
% # Simulate a current circulating around the hole in the ring.
% circulating_currents = {"hole": "1 mA"}

% solutions = sc.solve(
%     device=ring,
%     applied_field=None,
%     circulating_currents=circulating_currents
% )
% assert len(solutions) == 1 # Since there is only one layer
% solution = solutions[-1]

% solution.plot_currents(
%     figsize=(6, 7), cross_section_ys=[0], units="mA/um",
% )

% solution.plot_fields(
%     figsize=(6, 7), cross_section_ys=[0],
% )
% \end{minted}
% \captionof{listing}{Solve for the current and magnetic field distributions resulting from a total current of 1 mA flowing in our \mintinline{python}{ring} device.}
% \label{code:ring_circulating_current}
% \end{code}

\begin{figure}
\centering
\begin{subfigure}{.4\textwidth}
  \centering
  \includegraphics[width=\linewidth]{examples/images/ring/circular_ring_plot_currents.png}
  \caption{Circular ring sheet current.}
  \label{fig:circular_ring_plot_currents}
\end{subfigure}
\begin{subfigure}{.4\textwidth}
  \centering
  \includegraphics[width=\linewidth]{examples/images/ring/circular_ring_plot_fields.png}
  \caption{Circular ring magnetic field.}
  \label{fig:circular_ring_plot_fields}
\end{subfigure}

\begin{subfigure}{.4\textwidth}
  \centering
  \includegraphics[width=\linewidth]{examples/images/ring/square_ring_plot_currents.png}
  \caption{Square ring sheet current.}
  \label{fig:square_ring_plot_currents}
\end{subfigure}
\begin{subfigure}{.4\textwidth}
  \centering
  \includegraphics[width=\linewidth]{examples/images/ring/square_ring_plot_fields.png}
  \caption{Square ring magnetic field.}
  \label{fig:square_ring_plot_fields}
\end{subfigure}

\caption{Sheet current $\vec{J}$ and magnetic field $\mu_0H_z$ distributions for the circular (top) and square (bottom) ring calculated using Code Block~\ref{code:ring_circulating_current}.}
\label{fig:ring_circulating_current}
\end{figure}
